---
output:
  pdf_document: default
  html_document: default
---

# Data Analysis
### Multivariate regression for the Speaker Corpus, U.S.- conducted in May 2022
***

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
#Preliminaries
library("lmtest")
library("plm")
library(stargazer)
library(tidyverse)
library(broom)
theme_set(theme_classic())
setwd("/Users/charlottekaiser/Documents/uni/Hertie/master_thesis/00_data/50_analysis")
usa_reg<-read.csv("multivariate-reg-data-us.csv")
head(usa_reg)
```

### 1 Check states 
How many states does this dataset contain? 

```{r}
print("number of states:")
print(length(unique(usa_reg$state)))
```

### 2 Standardise DV
Constructing percentage version of the prevalence scores

```{r}
usa_reg$nat_sec_per<-100*(usa_reg$prev_nat_sec)
usa_reg$econ_per<-100*(usa_reg$prev_econ)
usa_reg
```



### 3 Regressions
#### 3.1 OLS 
Run a full model with all state individual effects and a model excluding states and checking the effect of a state being one of the states with the most active and reserve military members
```{r}
summary(ols_full_nat<-lm(nat_sec_per ~ party + gender + house_of_rep +(state),data=usa_reg))
summary(ols_nat <-lm(nat_sec_per ~ party + gender + house_of_rep + military_heavy ,data=usa_reg))
```
#### 3.2 Run regression diagnostics on full model 
```{r}
par(mfrow = c(2, 2))
plot(ols_full_nat)
# Cook's distance
plot(ols_full_nat, 4)
# Residuals vs Leverage
plot(ols_full_nat, 5)
```

#### 3.3 Fixed effects model
```{r}
summary(fe_nat <- plm(nat_sec_per ~  party + house_of_rep + gender + factor(state),
              data=usa_reg, index="state", model="within"))

```

```{r, warning = F, message = F}
getwd()
setwd("/Users/charlottekaiser/Documents/uni/Hertie/master_thesis/20_results/10_analysis/LDA_speaking-points")
getwd()
```

### 4 Save table output
```{r, warning = F, message = F}
# Preliminaries for table design. 
robust.order <- c("party", "house_of_rep", "gender", "military_heavy", "state") 
robust.label =  c( "Party Affiliation (1 = Democrat/0 = Republican)", "House of Representative (1 = Yes/0 = Senate)",
                   "Gender (1 = female/0 = male",
                   "Belongs to a state with the most active-duty and reserve members of the military (1 = Yes/0 = No)",
                   "State (Reference = Alabama)")


# Set up table with all three basic analyses components
stargazer(ols_nat, fe_nat, ols_full_nat,
          title="Multivariate OLS Regressions for topic 'National security'", 
          type = 'html', 
          out = "regressions_us.html",
          omit.stat=c("f", "ser"),
          style = "apsr", 
          order=paste0("^", robust.order , "$"), 
          digits=4, notes.align="l", 
          notes.append=FALSE,
          dep.var.labels ="",
          notes.label="",  
          column.labels = c("Military heavy", "Fixed effects", "Individual state effects"),
          model.numbers=TRUE, 
          covariate.labels =robust.label, 
          notes=c("Standard errors given in parentheses.",
          "***p<0.01; **p<0.05; *p<0.1.",
          "Prevalence measured in %"),
          summary.stat=("n"))

```